Network Configuration Synthesis with Abstract Topologies

### 2016-11-15 paper/abstraction/paper.tex
more edits

Worse, operators can never be sure that their templates correctly implement the policy. %
Formally verifying them is difficult; today's hand-generated templates have no particular semantics---which policies they implement and for which topologies---other than those of the configurations obtained from instantiating them.
%
Thus, operators validate templates by testing some concrete instantiations using
simulation or verification tools~\cite{feamster+:rcc, batfish, era, arc, bagpipe}. This testing is insufficient because large networks evolve continuously as
devices and links are added or taken offline for maintenance. Templates that
work for the current topology, may or may not work for future
topologies, and it is intractable to test all possible future topologies. Updating the templates, if found to not work for a future topology,
may cause trickle-down, network-wide configuration changes, which is highly
disruptive.
%Building sophisticated tools for validating templates is difficult

@@

  \end{minipage}
  \vspace{-.3em}
  \caption{\sysname core syntax.}
  \label{fig:syntax}
  %\vspace{-1em}
\end{figure}%

@@

  \caption{Example abstractions for HyperX and BCube.}
  %\vspace*{-1em}%
  \label{fig:example-abstractions}
\end{figure}

>>>>

Worse, operators can never be sure that their templates correctly implement the policy. %
Formally verifying them is difficult; today's hand-generated templates have no particular semantics---which policies they implement and for which topologies---other than those of the configurations obtained from instantiating them.
%
Thus, operators validate templates by testing some concrete instantiations using
simulation or verification tools~\cite{feamster+:rcc, batfish, era, arc, bagpipe}. This testing is insufficient because large networks evolve continuously as
devices and links are added or taken offline for maintenance. Templates that
work for the current topology, may or may not work for future
topologies, and it is intractable to test all possible future topologies. Updating the templates, if found to not work for a future topology,
may cause trickle-down, network-wide configuration changes, which is highly
disruptive in production networks with live traffic.
%Building sophisticated tools for validating templates is difficult

@@

  \end{minipage}
  \vspace{-.3em}
  \caption{\sysname core syntax.}
  \label{fig:syntax}
  %\vspace{-1.4em}
\end{figure}%

@@

  \caption{Example abstractions for HyperX and BCube.}
  \vspace*{-1em}%
  \label{fig:example-abstractions}
\end{figure}
